Computing Exact Restricted Isometry Constants via\\ Mixed Integer Semidefinite Programming

### 2016-03-13 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
paper: made conclusions more optimistic

\noindent
This paper shows that exact values of restricted isometry constants can be
computed via mixed-integer semidefinite programming. Although the used
matrices are necessarily small, we can significantly improve the bounds
computed by the semidefinite relaxations proposed in \cite{Asp08} and
\cite{Asp07}. Moreover, the results of this paper can be used to design
further approximations of the RIP, which might also be applicable for
larger matrices. On the negative side, the running time of the mixed-integer
semidefinite approach is significantly larger than the relaxation
of~\cite{Asp07}. On the positive side, it is faster and/or uses less memory
than the relaxation of \cite{Asp08} and it computes optimal constants!

For the future, the hope is that with the advancement of solving techniques
for mixed-integer semidefinite programs, the sizes of the matrices can be
significantly increased. The components to be improved include cutting
planes, primal heuristics, and branching rules.

>>>>

\noindent
This paper shows that exact values of restricted isometry constants can be
computed via mixed-integer semidefinite programming. The computed bounds
significantly improve the bounds computed by the semidefinite relaxations
proposed in~\cite{Asp07} and \cite{Asp08}. In conclusion, the relaxation of
\cite{Asp07} is fast to compute, but produces a gap of arround 90\,\% for
$\alpha_k$ and 23\,\% for $\beta_k$. If successfully solved, the relaxation
of \cite{Asp08} provides better bounds, but its running time is too large
to be used in practice. Moreover, directly solving~\eqref{MISDP} is often
faster and produces the exact value. Consequently, the relaxation
in~\cite{Asp08} should not be used in practice.

Still, the matrices currently handable by~\eqref{MISDP} are small. For the
future, the hope is that with the advancement of solving techniques for
mixed-integer semidefinite programs, the sizes of the matrices can be
significantly increased. The components to be improved include cutting
planes, primal heuristics, and branching rules.
